The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-26 SC-challenge.tex
wording change in a comment, added another comment

\katznote{Arfon, are the more that showed up in related work in the software citation activity?}

@@

Note that some software which is or could be captured as part of data provenance may not be cited.
Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
These statements may also be true for software products.
In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
\end{quote}
\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles}

>>>>

\katznote{Arfon, are there more that showed up in related work in the software citation activity?}

@@

Note that some software which is or could be captured as part of data provenance may not be cited.
Citation is a record of software that is important to the research outcome, where provenance is a record of all steps (including software) used to generated particular data within the research process.
This implies that for a data research product, provenance data will include all cited software, but not necessarily vice versa.
Similarly, the software metadata that is recorded as part of data provenance should be a superset of the metadata recorded as part of software citation.
And the data recorded for reproducibility should also be a superset of the metadata recorded as part of software citation.
These statements may also be true for software products.
In general, we intend the software citation principles to cover the minimum of what is necessary for software citation for the purpose of software identification.
Other use cases (e.g., provenance, reproducibility) may lead to additional requirements (i.e., enhanced metadata).
\end{quote}
\knnote{I worry that including this whole note is too much, especially if we plan to publish the principles} \katznote{feel free to edit to down}
